\section{System Analysis}
This chapter compares existing approaches and defines software requirements for the new system.

\subsection{Existing System (If Available)}
In many existing online PDF tools, users upload documents to remote servers for processing. The server performs transformation operations and returns result files. This architecture is operationally common, but it has constraints:
\begin{itemize}
  \item document data leaves the local device,
  \item performance depends on upload and download bandwidth,
  \item policies for file retention and deletion vary across providers.
\end{itemize}

\subsection{Need for New System}
A new system is needed where privacy-sensitive workflows do not require server upload. For academic, personal, and professional document handling, a local-first option reduces exposure and improves control over data flow.

\subsection{Detailed SRS (Software Requirement Specification)}
\textbf{Functional requirements:}
\begin{itemize}
  \item The system shall allow users to import one or more PDF files.
  \item The system shall provide operations such as merge, split, organize, and metadata inspection.
  \item The system shall export processed output files locally.
  \item The system shall run core PDF processing in the browser runtime.
\end{itemize}

\textbf{Non-functional requirements:}
\begin{itemize}
  \item Privacy: no mandatory server upload for core PDF operations.
  \item Usability: clear workflow with minimal user steps.
  \item Performance: acceptable response time for standard document sizes on modern hardware.
  \item Maintainability: modular code structure and automated tests.
\end{itemize}
